### 2019-06-12 fe_px_paper/fe_body_text.tex
Adding missing references. Adding test code to look for bib file in multiple locations for Overleaf compatibility.

However, the modeling of nuclear reactions in this mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies \cite{voinov, tavukcu}.  
% As 
Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
This was carried out 
% in a
using the thin-foil stacked-target technique to study proton-induced reactions on 
% experiment, using proton irradiation of 
natural iron foils with titanium and copper monitor foils.
% While recent work has been performed in the 40--100\,MeV energy region, t
This work seeks to complement 
% these measurements 
earlier measurements at 40--100\,MeV proton beam energies and extend them down to reaction thresholds, in order to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}. 
Furthermore, we are able to use a portion of the data we measured to gain insight into the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.

>>>>

However, the modeling of nuclear reactions in this mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.  
% As 
Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
This was carried out 
% in a
using the thin-foil stacked-target technique to study proton-induced reactions on 
% experiment, using proton irradiation of 
natural iron foils with titanium and copper monitor foils.
% While recent work has been performed in the 40--100\,MeV energy region, t
This work seeks to complement 
% these measurements 
earlier measurements at 40--100\,MeV proton beam energies and extend them down to reaction thresholds, in order to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}. 
Furthermore, we are able to use a portion of the data we measured to gain insight into the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.
